intRo

### 2016-06-21 presentations/user-2016/index.Rmd
add useR! talk

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare <br/> Iowa State University"
date: "August 11, 2015 <br> http://j.mp/intRo-JSM2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

@@

 - `R` is great, but requires students to have some knowledge/interest in programming
 - `JMP` is powerful, but too big
      - Licenses and inconsistent UI
 - New tools recently released to spark an interest in `R`
      - `Swirl` and DataCamp teach `R` programming
      - Project MOSAIC facilitates learning, but assumes knowledge of `R`
 - Want students to focus on data analysis rather than fight with software

## What is `intRo`?
 - A simple **web-based** application for performing basic data analysis and statistical routines
 - Built using `R` and `Shiny`
 - Extensible modular structure
 - Designed for a first statistics class student
 - Assists in the learning of statistics rather than acting as a stand-alone deliverer of statistics education

@@

# First look | http://intro-stats.com

@@

## Presenting choices (Cont'd)
<img src="images/graphical_table.png">

@@

## Producing clean code (Cont'd)
But how do we handle uploaded data?

```{r, eval=FALSE}
file.choose <- function () {
    return(input$data_own[,"datapath"])
}
```

Now we can provide to the user *and* the server:

```{r, eval=FALSE}
intro.data <- read.csv(file.choose())
```

@@

## What's next?
 - Module creation package
 - Server load
 - Use in other classes

## Module creation package
*Modularity* is a key feature of `intRo`, but module creation is currently:

@@

**Idea**: R package (with associated Shiny app?) to automate creation of `intRo` modules

>>>>

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare <br/> Iowa State University"
date: "June 28, 2016 <br> http://j.mp/intRo-JSM2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

@@

 - `R` is great, but requires students to have some knowledge/interest in programming
 - `JMP`, `Deducer`, `Rcmdr` are powerful, but too big
      - Licenses and inconsistent UI
 - New tools recently released to spark an interest in `R`
      - `Swirl` and DataCamp teach `R` programming
      - Project MOSAIC facilitates learning, but assumes knowledge of `R`
 - Want students to focus on data analysis rather than fight with software

## What is `intRo`?
 - A simple **web-based** application for performing basic data analysis and statistical routines and accompanying utility package
 - Built using `R` and `Shiny`
 - Extensible modular structure
 - Designed for a first statistics class student
 - Assists in the learning of statistics rather than acting as a stand-alone deliverer of statistics education

@@

# Take a look | http://intro-stats.com

# Deploying intRo

## intRo package

 - Installation: 
    ```{r eval=FALSE}
    devtools::install_github("rstudio/shinyapps") 
    devtools::install_github("gammarama/intRo")`
    ```

 - Functions:
    - `download_intRo` - Downloads a current revision of intRo to your machine
    - `run_intRo` - Runs an intRo session locally with the specified options
    - `deploy_intRo` - Deploys an instance of intRo to ShinyApps.io with the specified options

@@

@@

## Producing clean code (Cont'd)

 - Each call is wrapped in a function called `interpolate` [@interpolate]
    - Executes the given R code on the server
    - Writes the code executed to the script window at the bottom of intRo

```{r, eval=FALSE}
nonparametric_test <- function(intro.data, x, y, ...) {
  interpolate(~(wilcox.test(x = df$x, 
                            y = df$y, ...),
                  df = quote(intro.data),
                  x = x,
                  y = y,
                  ...,  
                  `_env` = environment(), 
                  file = "code_nonparametric.R")
}
```

@@

## Module creation
*Modularity* is a key feature of `intRo`, but module creation is currently:

@@

**Idea**: Include funcitonality in current R package to automate creation of `intRo` modules
